\myparagraph{Purpose}
Any special user can manage its profile from \textit{Data4Help} web site, in particular:
\begin{itemize}
  \item The special user can change some of its informations: its legal address, its billing address, its corporate e-mail address, the sector in which it operates;
  \item The special user can change all the data regarding its legal representative;
  \item The special user can see the data it has required and paied until this moment;
  \item The special user can see the payments it hasn't paied yet;
  \item The special user can change the preferred payment method;
  \item The special user can change his password;
  \item The special user can delete his profile.
\end{itemize}

\myparagraph{Scenario 1}
The executive director of PincoPallo SPA had a serious fight with the legal representative of its company, and he decided to fire him a week ago. Now that he has find a new legal he wants to change the data stored in his \textit{Data4Help} profile. He accesses to \textit{Data4Help} web site from his personal pc, he logs in with the company profile and clicks on "\textit{Edit profile}" button. Now he inserts all the information about the new legal in the matching fields and then clicks on "\textit{Submit changes}" button.

\myparagraph{Scenario 2}
AlphaAnalisi SPA wants to change the preferred payment method due to changes in its internal organization. It opens \textit{Data4Help} main page, logs in and accesses to its personal profile. It clicks on "\textit{Change payment method}" button and selects the new preferred method. Finally it clicks on "\textit{Submit changes}" button.

\myparagraph{Use Case}
The \textit{Special profile visualization} use case is analyzed in Table \ref{table:specialProfileVisualizationTable}. \\
The \textit{Modify personal information} use case is the same as the one analyzed for standard users. \\
The \textit{Change password} use case is the same as the one analyzed for standard users. \\
The \textit{Delete profile} use case is the same as the one analyzed for standard users. \\

\myparagraph{Functional requirements}
\begin{enumerate}
  \item The system must let the special user view his personal profile at anytime;
  \item The system must let the special user upload/change his personal information at anytime;
  \item The system must let the special user change his password only if the old one has been inserted correctly;
  \item The system must not let the special user change his password if the new one has not been inserted twice;
  \item The system must let the special user delete his profile at anytime;
  \item The system must require to confirm a deleting request;
  \item The system must not delete a profile if the choice isn't confirmed by the special user;
  \item The system must let the special user leave the editing profile process at anytime;
\end{enumerate}

\begin{center}
\begin{table}
\begin{tabular}{ | l | p{0.75\linewidth} | }
  \hline
    Actor & \textbf{Special user} \\ \hline
    Goal & \textbf{[G.3]} \\ \hline
    Input Condition & A \textbf{Special user} wants to view its profile\\ \hline
    Event Flow & \begin{minipage}[t]{0.7\textwidth}
      \begin{enumerate}
        \item The \textbf{Special user } opens \textit{Data4Help} web site;
        \item The \textbf{Special user} logs in;
        \item The \textbf{Special user} accesses to its personal area;
        \item The system shows to the \textbf{Special user} the data past required and paied data and the payments it hasn't paied yet.
      \end{enumerate}
    \smallskip
  \end{minipage} \\ \hline
  Output Condition & The \textbf{Special} views its profile with all the related information\\ \hline
  Exceptions & None \\ \hline
\end{tabular}
\caption{\textit{Special profile visualization} use case}
\label{table:specialProfileVisualizationTable}
\end{table}
\end{center}
