\myparagraph{Purpose}
For each \textit{Run}, that is present in the system, a \textit{Specator} or an \textit{User} must be able to watch it. The \textit{Spectator} or the \textit{User} could follow the positon, on the \textit{Run} path, of any person that has enroled the \textit{Run} and also he/she must be able to look at the placing table of the runners.

\myparagraph{Scenario 1}
Marco is a professional runner and play for a team, unfortunately one month ago he broke his leg. Today there is an important \textit{Run} and his teammates are enrolled. At 4 p.m., Marco will open \textit{Track4Run} app on his mobile phone, in the dashboard he will look for the today's \textit{Run}, he will click on it and immediately he will be "in the \textit{Run}"; he could follow his friend on the path (watching the position on the map) and clicking on the \textit{Placings} button he could see the current placing table.

\myparagraph{Scenario 2}
Andrea is a sport event planner. With his coworker Luca, they planned the "HOLI FUN Run" of the 7\textsuperscript{th} of July in Cremona. In the \textit{Run}'s day, Andrea was in France for a meeting so when the meeting ends he went back to his hotel, he opend his laptop and he went to \textit{Track4Run} web page, he searched, through the search bar, the \textit{Run} that unfortunately was just ended, however he was very happy because looking at the placing table he saw that his friend Marta won.

\myparagraph{Use Case}
The Run Watching is analyzed in Table \ref{table:visitRunTable}.

\myparagraph{Functional requirements}
\begin{enumerate}
  \item \textbf{Generic User} (that could be \textit{Specator} or \textit{User}) must be able to watch a \textit{Run} that is still in progress or ended;
  \item The system must continuously check the positon of the runner in order to keep the map and the placing table updated;
  \item The system must be able to show all the runners that enroled the \textit{Run} and their GPS position is enabled and nearby the path;
  \item The system must notify the end of a \textit{Run} to a \textbf{Specator} or an \textbf{User} that is watching it;
  \item The system must be able to compute the placing table through the GPS position of the runner enroled in the \textit{Run}.
\end{enumerate}

\begin{center}
\begin{table}
\begin{tabular}{ | l | p{0.75\linewidth} | }
  \hline
    Actor & \textbf{Generic User} that could be \textit{Specator} or \textit{User} \\ \hline
    Goal & \textbf{[G.13]} \\ \hline
    Input Condition & The \textbf{Generic User} want to watch a \textit{Run} \\ \hline
    Event Flow & \begin{minipage}[t]{0.7\textwidth}
      \begin{enumerate}
        \item The \textbf{Generic User} open \textit{Track4Run} service through mobile application or web application;
        \item The \textbf{Generic User} clicks on \textit{Watch a Run} button;
        \item The \textbf{Generic User} looks for a \textit{Run} through the search bar or looking to the proposed;
        \item The \textbf{Generic User} clicks on the \textit{Run} he/she wants to watch.
      \end{enumerate}
    \smallskip
  \end{minipage} \\ \hline
  Output Condition & The system loads the \textit{Run} environment (map, path and placing table) and  shows it to the \textbf{Generic User}. \\ \hline
  Exceptions & \begin{minipage}[t]{0.7\textwidth}
    \begin{itemize}
      \smallskip
      \item The \textbf{Generic User} looks for a \textit{Run} that is not present in the system, the system notifies the \textbf{Generic User} with a warning message;
      \item If the connection of the \textbf{Generic User} application is lost and the system couldn't be able to recover it the process goes back to step 3.
    \end{itemize}
    \smallskip
  \end{minipage}  \\ \hline
\end{tabular}
\caption{Run Watching use case}
\label{table:visitRunTable}
\end{table}
\end{center}
